---
title: "Bootstrap Resamlpling"
author: "Eden Molina"
date: "2/17/2021"
output: html_document
---
# Libraries
```{r}
library(tidyverse)
library(tidymodels)
```

# Load the data from GitHub
```{r}
historical_tuition <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-10/historical_tuition.csv')
historical_tuition %>% head()
```

# View the data
We can see there is some relation between public and private school tuition cost
```{r}
tuition_df <- historical_tuition %>% 
  # filter(tuition_type == '4 Year Constant') %>%
  pivot_wider(names_from = type,
              values_from = tuition_cost
              ) %>%
  na.omit() %>% 
  janitor::clean_names()

tuition_df %>% 
  ggplot(aes(public, private))+
  geom_point()+
  scale_y_continuous(labels=scales::dollar_format())+
  scale_x_continuous(labels=scales::dollar_format())+
  ggtitle("Private vs Public School Tuition")+
  xlab("Public School Tuition")+
  ylab("Private School Tuition")+
  theme_linedraw()+
  theme(axis.title=element_text(size=14,face="bold"),
        plot.title = element_text(size = 20, face = "bold"))+
  ggsave('/Users/edenmolina/Documents/Medium/Plots/1Bootstrap/Plot1.png',
         width = 8,
         height = 6)
```

# Baseline Model: Linear Model
Here we fit a linear model
0 is added so that we only fit for slope. If both groups should pay $0 at the $0 mark.
We can see that the estimated slope is 2.379 which means that for evey dollar a student at a public institution, a private student is expected to pay 2.379 times more.
```{r}
tuition_fit <- lm(private ~ 0 + public,
               data = tuition_df)

summary(tuition_fit)

tidy(tuition_fit)
```

# Use resampling to get a batter estimate of the relation
We will use bootstraping where we randomly draw with replacemant to create new datasets the same size as the original. This will simulate generating a new set of data. This frees us from the assumptions required in the linear model.
```{r}
set.seed(123)
tution_boot <- bootstraps(tuition_df,
                          times = 1e3,
                          apparent = TRUE)
```

## Fit a model to the 1000 resamplings
We fit a linear model to the models then create a new column with the tidied up results
```{r}
tuition_models <- tution_boot %>% 
  mutate(model = map(splits, ~lm(private ~ 0 + public,
               data = .) ),
         coef_inf = map(model, tidy))

tuition_coefs <- tuition_models %>% 
  unnest(coef_inf)
```

## View the distribution of extimates
This will help get an understanding of the relation between public and private tuition costs as well as the variability in the relation
```{r}
tuition_coefs %>% 
  ggplot(aes(estimate))+
  geom_histogram(alpha = .7)+
  ggtitle("Distribution of Estimated Slope")+
  xlab("Estimate")+
  ylab("Frequency")+
  theme_linedraw()+
  theme(axis.title=element_text(size=14,face="bold"),
        plot.title = element_text(size = 20, face = "bold"))+
  ggsave('/Users/edenmolina/Documents/Medium/Plots/1Bootstrap/Plot2.png',
         width = 8,
         height = 6)
  
```

### Get confidence intervals
The estimate after resampling is now 2.38 with lower bound 2.31 and upper bound of 2.46. This is similar to before: 2.379.
The results are very similar to before, this is likely because the relationship between the two is in fact linear.
```{r}
int_pctl(tuition_models,
         coef_inf)
```

## Vizualize the results of the models
```{r}
tuition_aug <- tuition_models %>% 
  # Sample only 500 bootstraps for viz
  sample_n(500) %>% 
  mutate(augmented = map(model, augment)) %>% 
  unnest(augmented)

# Vizualize the different fits we got from the simulated data
tuition_aug %>% 
  ggplot(aes(public, private))+
  geom_line(aes(y = .fitted, group = id), alpha = .1, color = 'grey')+
  geom_point()+
  scale_y_continuous(labels=scales::dollar_format())+
  scale_x_continuous(labels=scales::dollar_format())+
  ggtitle("500 of 1000 Slope Estimations from Bootstrap Resampling")+
  xlab("Public School Tuition")+
  ylab("Private School Tuition")+
  theme_linedraw()+
  theme(axis.title=element_text(size=14,face="bold"),
        plot.title = element_text(size = 15, face = "bold"))+
  ggsave('/Users/edenmolina/Documents/Medium/Plots/1Bootstrap/Plot3.png',
         width = 8,
         height = 6)
```


